Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

\subsection{Regression Model}
After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\
For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T\textsubscript t which repesents the variable {\itshape df\_nr\_of\_tweets} in our data set and B\textsubscript t which represents {\itshape df\_bpi\_closing\_price}. As defined in the previous section the selected otpimal time lag is 1. Given these information, the model equations can be written as follows:

>>>>

\subsection{VAR Regression Model}
After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\
For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T\textsubscript t which repesents the variable {\itshape df\_nr\_of\_tweets} in our data set and B\textsubscript t which represents {\itshape df\_bpi\_closing\_price}. As defined in the previous section the selected otpimal time lag is 1. Given these information, the model equations can be written as follows:
